\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-17 futurework.tex
change bwd/fwd layout

\revision{
\renewcommand\bugnum[2]{#1 {\scriptsize \em (#2)}}
\begin{figure}[t]
	\centering
	\begin{tabular}{cc}
	\multicolumn{2}{c}{\footnotesize
	\centering
	\begin{tabular}{|l|l||c|c|c|}
	\hline
	{\bf Bug} & {\bf Direction} & {\bf Time} & {\bf Backtracks} & {\bf Trace Length} \\
	\hline\hline
	\multirow{2}{*}{POBBLES vanish/vanish (a)} & Forwards & \bugnum{124.8}{4.9} & 1264 & 7 \\
	& Backwards & \bugnum{57.1}{1.7} & 376 & 11 \\
	\hline
	\multirow{2}{*}{POBBLES vanish/vanish (b)} & Forwards & \bugnum{106.3}{5.7} & 1030 & 7 \\
	& Backwards & \bugnum{51.5}{2.1} & 376 & 10 \\
	\hline
	\multirow{2}{*}{POBBLES wait/wait} & Forwards & \bugnum{62.6}{3.4} & 132 & 8 \\
	& Backwards & \bugnum{27.9}{0.8} & 17 & 13 \\
	\hline
	\multirow{2}{*}{POBBLES thread\_fork/vanish} & Forwards & \bugnum{21.4}{0.7} & 0 & 6 \\
	& Backwards & \bugnum{37.4}{1.1} & 70 & 6 \\
	\hline
	\multirow{2}{*}{LudicrOS vanish/vanish} & Forwards & \bugnum{14.7}{0.9} & 4 & 3 \\
	& Backwards & \bugnum{13.7}{0.7} & 3 & 7 \\
	\hline
	\multirow{2}{*}{LudicrOS yield/vanish} & Forwards & \bugnum{13}{0.9} & 3 & 3 \\
	& Backwards & \bugnum{11.4}{0.4} & 0 & 5 \\
	\hline
	\end{tabular}
	}
	\vspace{0.1in}
	\\
	\includegraphics[width=0.48\textwidth]{graphs/backwards-time.pdf} &
	\includegraphics[width=0.48\textwidth]{graphs/backwards-trace.pdf}
	\end{tabular}
	\caption{Comparison of forwards and backwards explorations for the six case study bugs (using decision points on \texttt{mutex\_lock} but not \texttt{mutex\_unlock}). In general, backwards exploration finds bugs faster, but forwards exploration produces shorter (more understandable) decision traces.}
	\label{fig:backwards}
\end{figure}
}

@@

\revision{Figure~\ref{fig:backwards} compares the tree explorations and resulting decision traces. The one exception is the POBBLES thread\_fork/vanish bug, which Landslide found immediately during forwards exploration, because the race actually required no forced preemptions to expose.}

>>>>

\revision{
\renewcommand\bugnum[2]{#1 {\scriptsize \em (#2)}}
\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|l|l||c|c|c|}
	\hline
	{\bf Bug} & {\bf Direction} & {\bf Time} & {\bf Backtracks} & {\bf Trace Length} \\
	\hline\hline
	\multirow{2}{*}{POBBLES vanish/vanish (a)} & Forwards & \bugnum{124.8}{4.9} & 1264 & 7 \\
	& Backwards & \bugnum{57.1}{1.7} & 376 & 11 \\
	\hline
	\multirow{2}{*}{POBBLES vanish/vanish (b)} & Forwards & \bugnum{106.3}{5.7} & 1030 & 7 \\
	& Backwards & \bugnum{51.5}{2.1} & 376 & 10 \\
	\hline
	\multirow{2}{*}{POBBLES wait/wait} & Forwards & \bugnum{62.6}{3.4} & 132 & 8 \\
	& Backwards & \bugnum{27.9}{0.8} & 17 & 13 \\
	\hline
	\multirow{2}{*}{POBBLES thread\_fork/vanish} & Forwards & \bugnum{21.4}{0.7} & 0 & 6 \\
	& Backwards & \bugnum{37.4}{1.1} & 70 & 6 \\
	\hline
	\multirow{2}{*}{LudicrOS vanish/vanish} & Forwards & \bugnum{14.7}{0.9} & 4 & 3 \\
	& Backwards & \bugnum{13.7}{0.7} & 3 & 7 \\
	\hline
	\multirow{2}{*}{LudicrOS yield/vanish} & Forwards & \bugnum{13}{0.9} & 3 & 3 \\
	& Backwards & \bugnum{11.4}{0.4} & 0 & 5 \\
	\hline
	\end{tabular}
	\caption{Comparison of forwards and backwards explorations for the six case study bugs (using decision points on \texttt{mutex\_lock} but not \texttt{mutex\_unlock}).}
	\label{fig:backwards}
\end{table}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{graphs/backwards-time.pdf}
	\hspace{0.02\textwidth}
	\includegraphics[width=0.48\textwidth]{graphs/backwards-trace.pdf}
	\caption{In general, backwards exploration finds bugs faster, but forwards exploration produces shorter (more understandable) decision traces.}
	\label{fig:backwards-graphs}
\end{figure}
}

@@

\revision{Table~\ref{fig:backwards} and Figure~\ref{fig:backwards-graphs} compare the tree explorations and resulting decision traces. The one exception is the POBBLES thread\_fork/vanish bug, which Landslide found immediately during forwards exploration, because the race actually required no forced preemptions to expose.}
